WFH and broadband speed (title needs rework)

### 2020-12-15 paper/v1/broadband.speed.covid.Rmd
minor changes

The identification strategy is as follows.
Based on the outcomes of the time-series clustering, we identify $J$ distinct
and crisp clusters.
We then regress this cluster membership against a vector $X_{i}$ of
socio-economic and geographic variables, which are discussed in detail in
Section \ref{#sec:4.2}.
This analysis enables us to provide a more nuanced understanding of how
telecommuting and technology intersect at a time of extreme demand, and what
lessons this time has for a future where telecommuting is likely to remain a
common means of accessing work and broadband services, as well as infrastructure,
must be fit for purpose.

@@

clustersLADup <- clustersLADup %>% 
  mutate(across(4:7, round, 3))

stargazer(clustersLADup[1:7],
          summary = F,
          font.size = "footnotesize",
          type = "latex",
          header = F, 
          covariate.labels=c("Cluster",
                             "N. of LADs",
                             "LAD population",
                             "mean speed",
                             "SD speed",
                             "mean AM speed",
                             "mean PM speed"),
                             #"AM_slower",
                             #"SDtoMean"),
          rownames = F,
          no.space=TRUE,
          column.sep.width = "0pt", 
          notes = "Note: All speed measures are upload speeds",
          title = "Upload speed cluster characteristics\\label{up.cluster.descr}")
```
The largest two clusters, comprising $281$ local authorities and almost $50$ million 
people, fall into clusters $6$ and cluster $13$.
Cluster $13$ has one of the lowest aggregate mean upload speed of any of the clusters,
and the second highest ratio of the standard deviation to the mean.
This suggests that those living in local authorities in this cluster experienced 
some of the lowest quality broadband services in terms of upload speeds in the UK.
However, the variation in upload speeds in cluster $13$, 
which can be an indication of its reliability, does not seem to disproportionately 
affect the morning peak from 9:00-10:59, as upload speeds are, on average, 
only $2.6$% slower than in the evening peak period between 19:00 and 20:59.
Although cluster $13$ does include some rural, remote areas of the country, 
such as Northwest Scotland, Cornwall and Powys in Wales as shown on Figure \ref{map.up.clusters},
it also includes the major metropolitan centres of Bristol, Liverpool, 
and Newcastle, as well as nine (of $32$) London Boroughs and plenty of home county 
and suburban areas.
Meanwhile, those living in cluster $6$ experience aggregate mean upload speeds of 
about $1$Mb/s faster than those in cluster $13$, but still lower than the other three
large clusters and most of the smaller clusters, 
suggesting a middling quality of service.
However, the time profile for cluster $6$ in Figure $3$a shows that upload speeds 
drop quickly from $6:00$ to 7:00 on a Monday and peak between 23:00 and midnight 
on Wednesday and Thursday, but tend to be lower during the working day.
Indeed, those in cluster $6$, including people living in Birmingham, Leeds and 
Sheffield, in $12$ London Boroughs, and many suburban areas and smaller cities like
Cardiff, Oxford and Cambridge experience mean upload speeds in the morning that are
$4.4$% lower than in the evening.
This lower level of reliability may be as a result of increased demand, 
e.g. for telecommuting, especially as there are few truly remote areas 
in this cluster.

@@

However, whilst the difference in experienced mean upload speeds between 9:00-10:59
and 19:00-20:59 in cluster $6$ is greater than in any of the other large clusters, 
it is smaller than this difference in all the clusters shown in Figure \ref{UpClusterL}.
Whilst this may suggest a lack of reliability, especially considering the large
spikes and dips in these clusters, the statistics in Table $1$ show 
a more varied picture.
The experienced upload speeds in cluster $1$ are the second slowest of any cluster,
the ratio of standard deviation to mean is the highest, as is the ratio of speeds 
in the morning compared to the evening peak hours analysed.
The five, mainly rural authorities in this cluster clearly lack broadband resilience,
for telecommuting or otherwise.
Home to almost $3.5$ thousand people, the districts are scattered around the country:
Ceredigion in West Wales, Darlington in the Northeast, Eden between the Lake District
and the North Penines, Rossendale in the Northwest, and Rutland in the East Midlands.
In comparison, clusters $3$ and $10$ have relatively high mean upload speeds, and 
low standard deviations, suggesting reliability and resilience, 
as well as quality broadband services, despite slower speeds in the morning peak.
Like cluster $6$, is this also a sign of increased telecommuting?
The eight LADs in clusters $3$ and $10$ are home to over one million people,
and are all more urban and suburban than cluster $1$, including the London Borough 
of Newham, the Southeast commuter towns of Harlow and Luton, the Birmingham suburbs 
of Bromsgrove and Cannock Chase, Dundee City, and the towns of Eastbourne and Corby.

@@

stargazer(aux.up, 
          type = "latex",
          nobs = T,
          digits = 3,
          font.size = "tiny",
          float.env = "sidewaystable",
          dep.var.caption = "",
          title = "Auxiliary multinomial regression of upload speed clusters on socio-economic and geographic LAD variables\\label{aux}",
          header = F,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "managerial jobs, 2020",
                             "tech jobs, 2020",
                             "skilled trade jobs, 2020",
                             "professional jobs, 2020",
                             "administrative jobs, 2020",
                             "leisure jobs, 2020",
                             "machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "NVQ4+",
                             "AM tests per hab., 2020",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs
                            , n.obs, n.obs))))
```

Clusters $3$, $9$, $10$ and $11$ seem to benefit most from high quality and 
resilient broadband services.
The dips in mean upload speeds in clusters $6$, $3$ and $10$ during the morning
peak are suggestive of more use during the working day, and potentially more
telecommuting.
Using auxiliary regressions, we test whether the clusters that have higher mean
speeds and more reliable services are more urban, more wealthy, and / or more likely 
to benefit from a choice of high quality internet services.
We also measure which of our clusters are more likely to have a higher proportion of 
occupations which enable telecommuting because of the nature of the work.
The results of these auxiliary regressions are presented in Table \ref{aux}.
The dependent variable is the LAD cluster membership as described in Section \ref{#sec:3}
and equation \ref{eq1} and each column represent a different cluster.
The reference case is cluster $4$, which includes the local authority of Hambleton
in North Yorkshire, a rural area of just over ninety thousand people.
Mean, experienced upload speeds in cluster $4$ are close to both the average speeds
for the $13$ clusters ($9.9$Mb/s) and the pre-clustered average for the whole sample
($9.3$Mb/s).
The standard deviation for cluster $4$ and the ratio of evening to morning peak speeds
are indications of worse reliability than many of the other clusters.
Hence, the results in Table \ref{aux} should be seens as relative
rather than absolute probabilities.

>>>>

The identification strategy is as follows.
Based on the outcomes of the time-series clustering, we identify $J$ distinct
and crisp clusters.
We then regress this cluster membership against a vector $X_{i}$ of
socio-economic and geographic variables, which are discussed in detail in
the relevant [section](#sec:4.2).
This analysis enables us to provide a more nuanced understanding of how
telecommuting and technology intersect at a time of extreme demand, and what
lessons this time has for a future where telecommuting is likely to remain a
common means of accessing work and broadband services, as well as infrastructure,
must be fit for purpose.

@@

clustersLADup <- clustersLADup %>% 
  mutate(across(4:7, round, 0))

stargazer(clustersLADup[1:7],
          summary = F,
          font.size = "footnotesize",
          type = "latex",
          header = F,
          digit.separator = ",",
          digit.separate = c(3,3),
          covariate.labels=c("Cluster",
                             "N. of LADs",
                             "LAD population",
                             "mean speed",
                             "SD speed",
                             "mean AM speed",
                             "mean PM speed"),
                             #"AM_slower",
                             #"SDtoMean"),
          rownames = F,
          no.space=TRUE,
          column.sep.width = "0pt", 
          notes = "Note: All speed measures are upload speeds",
          title = "Upload speed cluster characteristics\\label{up.cluster.descr}")
```
The largest two clusters, comprising $281$ local authorities and almost $50$ million 
people, fall into clusters $6$ and cluster $13$.
Cluster $13$ has one of the lowest aggregate mean upload speed of any of the clusters,
and the second highest ratio of the standard deviation to the mean.
This suggests that those living in local authorities in this cluster experienced 
some of the lowest quality broadband services in terms of upload speeds in the UK.
However, the variation in upload speeds in cluster $13$, 
which can be an indication of its reliability, does not seem to disproportionately 
affect the morning peak from 9:00-10:59, as upload speeds are, on average, 
only $2.6$% slower than in the evening peak period between 19:00 and 20:59.
Although cluster $13$ does include some rural, remote areas of the country, 
such as Northwest Scotland, Cornwall and Powys in Wales as shown on Figure \ref{map.up.clusters},
it also includes the major metropolitan centres of Bristol, Liverpool, 
and Newcastle, as well as nine (of $32$) London Boroughs and plenty of home county 
and suburban areas.
Meanwhile, those living in cluster $6$ experience aggregate mean upload speeds of 
about $1$Mb/s faster than those in cluster $13$, but still lower than the other three
large clusters and most of the smaller clusters, 
suggesting a middling quality of service.
However, the time profile for cluster $6$ in Figure $3$a shows that upload speeds 
drop quickly from $6:00$ to 7:00 on a Monday and peak between 23:00 and midnight 
on Wednesday and Thursday, but tend to be lower during the working day.
Indeed, those in cluster $6$, including people living in Birmingham, Leeds and 
Sheffield, in $12$ London Boroughs, and many suburban areas and smaller cities like
Cardiff, Oxford and Cambridge experience mean upload speeds in the morning that are
$4.4$% lower than in the evening.
This lower level of reliability may be as a result of increased demand, 
e.g. for telecommuting, especially as there are few truly remote areas 
in this cluster.

@@

However, whilst the difference in experienced mean upload speeds between 9:00-10:59
and 19:00-20:59 in cluster $6$ is greater than in any of the other large clusters, 
it is smaller than this difference in all the clusters shown in Figure \ref{UpClusterL}.
Whilst this may suggest a lack of reliability, especially considering the large
spikes and dips in these clusters, the statistics in Table \ref{up.cluster.descr} show 
a more varied picture.
The experienced upload speeds in cluster $1$ are the second slowest of any cluster,
the ratio of standard deviation to mean is the highest, as is the ratio of speeds 
in the morning compared to the evening peak hours analysed.
The five, mainly rural authorities in this cluster clearly lack broadband resilience,
for telecommuting or otherwise.
Home to almost $3.5$ thousand people, the districts are scattered around the country:
Ceredigion in West Wales, Darlington in the Northeast, Eden between the Lake District
and the North Penines, Rossendale in the Northwest, and Rutland in the East Midlands.
In comparison, clusters $3$ and $10$ have relatively high mean upload speeds, and 
low standard deviations, suggesting reliability and resilience, 
as well as quality broadband services, despite slower speeds in the morning peak.
Like cluster $6$, is this also a sign of increased telecommuting?
The eight LADs in clusters $3$ and $10$ are home to over one million people,
and are all more urban and suburban than cluster $1$, including the London Borough 
of Newham, the Southeast commuter towns of Harlow and Luton, the Birmingham suburbs 
of Bromsgrove and Cannock Chase, Dundee City, and the towns of Eastbourne and Corby.

@@

stargazer(aux.up, 
          type = "latex",
          nobs = T,
          digits = 3,
          font.size = "tiny",
          float.env = "sidewaystable",
          dep.var.caption = "",
          title = "Auxiliary multinomial regression of upload speed clusters on socio-economic and geographic LAD variables\\label{aux}",
          header = F,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "managerial jobs, 2020",
                             "tech jobs, 2020",
                             "skilled trade jobs, 2020",
                             "professional jobs, 2020",
                             "administrative jobs, 2020",
                             "leisure jobs, 2020",
                             "machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "NVQ4+",
                             "AM tests per hab., 2020",
                             "Virgin Media \\%, 2020"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs
                            , n.obs, n.obs))))
```

Clusters $3$, $9$, $10$ and $11$ seem to benefit most from high quality and 
resilient broadband services.
The dips in mean upload speeds in clusters $6$, $3$ and $10$ during the morning
peak are suggestive of more use during the working day, and potentially more
telecommuting.
Using auxiliary regressions, we test whether the clusters that have higher mean
speeds and more reliable services are more urban, more wealthy, and / or more likely 
to benefit from a choice of high quality internet services.
We also measure which of our clusters are more likely to have a higher proportion of 
occupations which enable telecommuting because of the nature of the work.
The results of these auxiliary regressions are presented in Table \ref{aux}.
The dependent variable is the LAD cluster membership as described in the 
[Methods and data](#sec:3) section
and equation \ref{eq1} and each column represent a different cluster.
The reference case is cluster $4$, which includes the local authority of Hambleton
in North Yorkshire, a rural area of just over ninety thousand people.
Mean, experienced upload speeds in cluster $4$ are close to both the average speeds
for the $13$ clusters ($9.9$Mb/s) and the pre-clustered average for the whole sample
($9.3$Mb/s).
The standard deviation for cluster $4$ and the ratio of evening to morning peak speeds
are indications of worse reliability than many of the other clusters.
Hence, the results in Table \ref{aux} should be seens as relative
rather than absolute probabilities.

### 2020-12-15 paper/v1/broadband.speed.covid.tex
minor changes

The identification strategy is as follows. Based on the outcomes of the
time-series clustering, we identify \(J\) distinct and crisp clusters.
We then regress this cluster membership against a vector \(X_{i}\) of
socio-economic and geographic variables, which are discussed in detail
in Section \ref{#sec:4.2}. This analysis enables us to provide a more
nuanced understanding of how telecommuting and technology intersect at a
time of extreme demand, and what lessons this time has for a future
where telecommuting is likely to remain a common means of accessing work
and broadband services, as well as infrastructure, must be fit for
purpose.

@@

\begin{table}[!htbp] \centering 
  \caption{Upload speed cluster characteristics\label{up.cluster.descr}} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{0pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Cluster & N. of LADs & LAD population & mean speed & SD speed & mean AM speed & mean PM speed \\ 
\hline \\[-1.8ex] 
1 & 5 & 343100 & 8557.389 & 6138.998 & 7746.892 & 9562.508 \\ 
2 & 2 & 265600 & 10921.69 & 6686.872 & 9674.043 & 10645.43 \\ 
3 & 4 & 474700 & 10200.753 & 5658.418 & 9470.446 & 11236.237 \\ 
4 & 1 & 91100 & 9688.899 & 6121.587 & 7816.234 & 9689.224 \\ 
5 & 1 & 79800 & 10126.506 & 6024.124 & 9030.22 & 11100.605 \\ 
6 & 155 & 29535700 & 9396.565 & 5839.097 & 9161.33 & 9580.422 \\ 
7 & 4 & 559800 & 10119.495 & 6102.311 & 9813.353 & 11070.093 \\ 
8 & 5 & 436300 & 9428.931 & 6254.047 & 8681.534 & 10434.339 \\ 
9 & 32 & 6355500 & 10878.131 & 5957.156 & 10831.557 & 11070.88 \\ 
10 & 4 & 699600 & 10795.469 & 6005.111 & 9257.855 & 10697.492 \\ 
11 & 33 & 5771400 & 10845.045 & 5936.36 & 10780.877 & 10987.827 \\ 
12 & 10 & 1544900 & 9550.756 & 6165.524 & 9254.436 & 9047.503 \\ 
13 & 126 & 20277700 & 8392.451 & 5849.227 & 8298.513 & 8521.828 \\ 
\hline \\[-1.8ex] 
\multicolumn{7}{l}{Note: All speed measures are upload speeds} \\ 
\end{tabular} 
\end{table}

@@

However, whilst the difference in experienced mean upload speeds between
9:00-10:59 and 19:00-20:59 in cluster \(6\) is greater than in any of
the other large clusters, it is smaller than this difference in all the
clusters shown in Figure \ref{UpClusterL}. Whilst this may suggest a
lack of reliability, especially considering the large spikes and dips in
these clusters, the statistics in Table \(1\) show a more varied
picture. The experienced upload speeds in cluster \(1\) are the second
slowest of any cluster, the ratio of standard deviation to mean is the
highest, as is the ratio of speeds in the morning compared to the
evening peak hours analysed. The five, mainly rural authorities in this
cluster clearly lack broadband resilience, for telecommuting or
otherwise. Home to almost \(3.5\) thousand people, the districts are
scattered around the country: Ceredigion in West Wales, Darlington in
the Northeast, Eden between the Lake District and the North Penines,
Rossendale in the Northwest, and Rutland in the East Midlands. In
comparison, clusters \(3\) and \(10\) have relatively high mean upload
speeds, and low standard deviations, suggesting reliability and
resilience, as well as quality broadband services, despite slower speeds
in the morning peak. Like cluster \(6\), is this also a sign of
increased telecommuting? The eight LADs in clusters \(3\) and \(10\) are
home to over one million people, and are all more urban and suburban
than cluster \(1\), including the London Borough of Newham, the
Southeast commuter towns of Harlow and Luton, the Birmingham suburbs of
Bromsgrove and Cannock Chase, Dundee City, and the towns of Eastbourne
and Corby.

@@

 % of Virgin Media connections & $-$0.044$^{***}$ & 1.578$^{***}$ & 1.210$^{***}$ & 0.248$^{***}$ & $-$1.724$^{***}$ & $-$0.242$^{***}$ & 3.109$^{***}$ & $-$0.085$^{***}$ & 1.214$^{***}$ & $-$3.889$^{***}$ & $-$0.745$^{***}$ \\ 

@@

Clusters \(3\), \(9\), \(10\) and \(11\) seem to benefit most from high
quality and resilient broadband services. The dips in mean upload speeds
in clusters \(6\), \(3\) and \(10\) during the morning peak are
suggestive of more use during the working day, and potentially more
telecommuting. Using auxiliary regressions, we test whether the clusters
that have higher mean speeds and more reliable services are more urban,
more wealthy, and / or more likely to benefit from a choice of high
quality internet services. We also measure which of our clusters are
more likely to have a higher proportion of occupations which enable
telecommuting because of the nature of the work. The results of these
auxiliary regressions are presented in Table \ref{aux}. The dependent
variable is the LAD cluster membership as described in Section
\ref{#sec:3} and equation \ref{eq1} and each column represent a
different cluster. The reference case is cluster \(4\), which includes
the local authority of Hambleton in North Yorkshire, a rural area of
just over ninety thousand people. Mean, experienced upload speeds in
cluster \(4\) are close to both the average speeds for the \(13\)
clusters (\(9.9\)Mb/s) and the pre-clustered average for the whole
sample (\(9.3\)Mb/s). The standard deviation for cluster \(4\) and the
ratio of evening to morning peak speeds are indications of worse
reliability than many of the other clusters. Hence, the results in Table
\ref{aux} should be seens as relative rather than absolute
probabilities.

>>>>

The identification strategy is as follows. Based on the outcomes of the
time-series clustering, we identify \(J\) distinct and crisp clusters.
We then regress this cluster membership against a vector \(X_{i}\) of
socio-economic and geographic variables, which are discussed in detail
in the relevant \protect\hyperlink{sec:4.2}{section}. This analysis
enables us to provide a more nuanced understanding of how telecommuting
and technology intersect at a time of extreme demand, and what lessons
this time has for a future where telecommuting is likely to remain a
common means of accessing work and broadband services, as well as
infrastructure, must be fit for purpose.

@@

\begin{table}[!htbp] \centering 
  \caption{Upload speed cluster characteristics\label{up.cluster.descr}} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{0pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Cluster & N. of LADs & LAD population & mean speed & SD speed & mean AM speed & mean PM speed \\ 
\hline \\[-1.8ex] 
1 & 5 & 343100 & 8557 & 6139 & 7747 & 9563 \\ 
2 & 2 & 265600 & 10922 & 6687 & 9674 & 10645 \\ 
3 & 4 & 474700 & 10201 & 5658 & 9470 & 11236 \\ 
4 & 1 & 91100 & 9689 & 6122 & 7816 & 9689 \\ 
5 & 1 & 79800 & 10127 & 6024 & 9030 & 11101 \\ 
6 & 155 & 29535700 & 9397 & 5839 & 9161 & 9580 \\ 
7 & 4 & 559800 & 10119 & 6102 & 9813 & 11070 \\ 
8 & 5 & 436300 & 9429 & 6254 & 8682 & 10434 \\ 
9 & 32 & 6355500 & 10878 & 5957 & 10832 & 11071 \\ 
10 & 4 & 699600 & 10795 & 6005 & 9258 & 10697 \\ 
11 & 33 & 5771400 & 10845 & 5936 & 10781 & 10988 \\ 
12 & 10 & 1544900 & 9551 & 6166 & 9254 & 9048 \\ 
13 & 126 & 20277700 & 8392 & 5849 & 8299 & 8522 \\ 
\hline \\[-1.8ex] 
\multicolumn{7}{l}{Note: All speed measures are upload speeds} \\ 
\end{tabular} 
\end{table}

@@

However, whilst the difference in experienced mean upload speeds between
9:00-10:59 and 19:00-20:59 in cluster \(6\) is greater than in any of
the other large clusters, it is smaller than this difference in all the
clusters shown in Figure \ref{UpClusterL}. Whilst this may suggest a
lack of reliability, especially considering the large spikes and dips in
these clusters, the statistics in Table \ref{up.cluster.descr} show a
more varied picture. The experienced upload speeds in cluster \(1\) are
the second slowest of any cluster, the ratio of standard deviation to
mean is the highest, as is the ratio of speeds in the morning compared
to the evening peak hours analysed. The five, mainly rural authorities
in this cluster clearly lack broadband resilience, for telecommuting or
otherwise. Home to almost \(3.5\) thousand people, the districts are
scattered around the country: Ceredigion in West Wales, Darlington in
the Northeast, Eden between the Lake District and the North Penines,
Rossendale in the Northwest, and Rutland in the East Midlands. In
comparison, clusters \(3\) and \(10\) have relatively high mean upload
speeds, and low standard deviations, suggesting reliability and
resilience, as well as quality broadband services, despite slower speeds
in the morning peak. Like cluster \(6\), is this also a sign of
increased telecommuting? The eight LADs in clusters \(3\) and \(10\) are
home to over one million people, and are all more urban and suburban
than cluster \(1\), including the London Borough of Newham, the
Southeast commuter towns of Harlow and Luton, the Birmingham suburbs of
Bromsgrove and Cannock Chase, Dundee City, and the towns of Eastbourne
and Corby.

@@

 Virgin Media \%, 2020 & $-$0.044$^{***}$ & 1.578$^{***}$ & 1.210$^{***}$ & 0.248$^{***}$ & $-$1.724$^{***}$ & $-$0.242$^{***}$ & 3.109$^{***}$ & $-$0.085$^{***}$ & 1.214$^{***}$ & $-$3.889$^{***}$ & $-$0.745$^{***}$ \\ 

@@

Clusters \(3\), \(9\), \(10\) and \(11\) seem to benefit most from high
quality and resilient broadband services. The dips in mean upload speeds
in clusters \(6\), \(3\) and \(10\) during the morning peak are
suggestive of more use during the working day, and potentially more
telecommuting. Using auxiliary regressions, we test whether the clusters
that have higher mean speeds and more reliable services are more urban,
more wealthy, and / or more likely to benefit from a choice of high
quality internet services. We also measure which of our clusters are
more likely to have a higher proportion of occupations which enable
telecommuting because of the nature of the work. The results of these
auxiliary regressions are presented in Table \ref{aux}. The dependent
variable is the LAD cluster membership as described in the
\protect\hyperlink{sec:3}{Methods and data} section and equation
\ref{eq1} and each column represent a different cluster. The reference
case is cluster \(4\), which includes the local authority of Hambleton
in North Yorkshire, a rural area of just over ninety thousand people.
Mean, experienced upload speeds in cluster \(4\) are close to both the
average speeds for the \(13\) clusters (\(9.9\)Mb/s) and the
pre-clustered average for the whole sample (\(9.3\)Mb/s). The standard
deviation for cluster \(4\) and the ratio of evening to morning peak
speeds are indications of worse reliability than many of the other
clusters. Hence, the results in Table \ref{aux} should be seens as
relative rather than absolute probabilities.
